Appendix S1: Supporting Information

### 2021-08-24 ms/SI.Rmd
Update MS
Add ref for Loiseau 2020
Update MS
- Use CVD-friendly colors for maps
- Make coastline thinner to improve visibility
- Move color palette setup to ms_functions.R

```{r setup-si, include = FALSE, cache = FALSE}
# Load functions only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)

# Load packages only used when knitting Rmd
library(kableExtra)
library(scales)
library(ggtree)
```

@@

```{r map-plot-prep}
# Change cluster to factor
biodiv_ferns_spatial <- biodiv_ferns_spatial %>%
  mutate(taxonomic_cluster = as.factor(taxonomic_cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  mutate(phylo_cluster = as.factor(phylo_cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  # Add redundancy
  mutate(redundancy = 1 - (richness/abundance))

# Download high-res map of Japan,
# crop to spatial div results area
japan <- sf::st_crop(japan_shp, sf::st_bbox(biodiv_ferns_spatial))

@@

biodiv_ferns_endemic_spatial <- sf::st_set_crs(biodiv_ferns_endemic_spatial, japan_crs)

biodiv_ferns_spatial <- sf::st_set_crs(biodiv_ferns_spatial, japan_crs)

@@

# Set color palettes
# - Randomization test significance
signif_cols <-
  c(
    "> 0.99" = "#e31a1c", 
    "> 0.975" = "#fb9a99",
    "< 0.01" = "#1f78b4", 
    "< 0.025" = "#a6cee3",
    "not significant" = "#ffffcc"
  )
# - CANAPE
canape_cols <-
  c(
    "neo" = "#e31a1c", 
    "paleo" = "#1f78b4",
    "mixed" = "#6a51a3",
    "super" = "#4a1486",
    "not significant" = "#ffffcc"
  )
# - Bioregions
bioregion_cols <- rcartocolor::carto_pal(9, "Bold")[1:8] %>%
  set_names(1:8)

@@

**`r s_figure("tree")`**. Time tree of native Japanese ferns and lycophytes, excluding hybrids. Points at nodes indicate bootstrap support. Scalebar 100 my.

@@

# Generate final plot
modelfit_plot_list <- 
  model_fits_not_ult %>%
  mutate(
    signif_var = str_replace_all(resp_var, "_obs_z", "_signif"),
    resp_var_print = case_when(
      resp_var == "richness" ~ "Richness (no. spp.)",
      TRUE ~ str_to_upper(resp_var) %>% word(1, 1, "_") %>% paste("SES of", .)
    ),
    model_data = list(biodiv_ferns_used_for_model)) %>%
  left_join(model_subplot_order, by = c("resp_var", "indep_var")) %>%
  arrange(order) %>%
  pmap(plot_fits)

>>>>

```{r setup-si, include = FALSE, cache = FALSE, eval = TRUE}
# Load packages only used when knitting Rmd
library(kableExtra)
library(scales)
library(ggtree)
library(RColorBrewer)
# Load functions and variables only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

```{r map-plot-prep}
# Download high-res map of Japan,
# crop to spatial div results area
japan <- sf::st_crop(japan_shp, sf::st_bbox(biodiv_ferns_spatial))

@@

# Format biodiv_ferns_spatial data
biodiv_ferns_spatial <-
  biodiv_ferns_spatial %>% 
  # Set CRS
  sf::st_set_crs(japan_crs) %>%
  # Set order of factor levels for plotting
  mutate(
    endem_type = factor(endem_type, levels = c("neo", "paleo", "not significant", "mixed", "super")),
    # can ignore warning about unknown levels, since they don't exist in all variables but that's OK
    across(
      contains("signif"),
      ~fct_relevel(.x, "< 0.01",  "< 0.025", "not significant", "> 0.975", "> 0.99")
    )
  )

biodiv_ferns_endemic_spatial <-
  biodiv_ferns_endemic_spatial %>% 
  # Set CRS
  sf::st_set_crs(japan_crs) %>%
  # Set order of factor levels for plotting
  mutate(
    endem_type = factor(endem_type, levels = c("neo", "paleo", "not significant", "mixed", "super"))
    )

@@

@@

**`r s_figure("tree")`**. Time tree of native Japanese ferns and lycophytes, excluding hybrids. Points at nodes indicate bootstrap support. Scalebar 100 my. Tree visualized with the `r pack("ggtree")` R package [@Yu2017].

@@

# Generate final plot
modelfit_plot_list <- 
  model_fits_not_ult %>%
  mutate(
    signif_var = str_replace_all(resp_var, "_obs_z", "_signif"),
    resp_var_print = case_when(
      resp_var == "richness" ~ "Richness (no. spp.)",
      TRUE ~ str_to_upper(resp_var) %>% word(1, 1, "_") %>% paste("SES of", .)
    ),
    model_data = list(biodiv_ferns_used_for_model),
    signif_cols = list(signif_cols)) %>%
  left_join(model_subplot_order, by = c("resp_var", "indep_var")) %>%
  arrange(order) %>%
  pmap(plot_fits)
